Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Implies That Modelling This Situation Using Other Models Would Be Better

### 2024-12-14 paper/paper.qmd
Fix some minor mistakes

---
title: "Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Implies That Modelling This Situation Using Other Models Would Be Better"
author: 
  - Kevn Shao
thanks: "Code and data are available at: https://github.com/KevinShao1357/Toronto_Daily_Shelter_And_Overnight_Service_Modelling.git."
date: today
date-format: long
abstract: "Recently, the Canadian government expresses interest in continuous investment in government faculties providing daily shelter and/or overnight services. With the aim to evaluate the validity of predicting the occupied beds at a related faculties at a day, which can reflect the demand of such services at such locations, a multivariate linear regression model is constructed, with the city to Downtown Toronto, and the gender and age set to Mixed Adults. Five predictor variables are used, including two numerical variables, occupancy rate and capacity, and three categorical variables, including classification, service types, and program types. The final results showed likely violations of linearity assumptions such as homoscedasticity and normality of errors, and suggests that we may need to consider either proceed deeper in the linear regression model by adding nonlinear terms for predictor variables, identifying and deleting influential points, and/or consider the weighted-least squares (WLS) method, or consider switching to other more-flexible model types."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Downtown Toronto has the most shelters in all the cities (of GTA(Greater Toronto Area)) in this dataset, so we also conclude that Downtown Toronto is the most representative of all the provided cities, so we then filter out the cleaned data so it only contains shelters in Downtown Toronto.

@@

```{r}
#| label: tbl-table9
#| tbl-cap: "Coefficients of the Final Model"
#| echo: false
#| warning: false
#| message: false

>>>>

---
title: "Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Implies That Modelling This Situation Using Other Models Would Be Better"
author: 
  - Kevn Shao
thanks: "Code and data are available at: https://github.com/KevinShao1357/Toronto_Daily_Shelter_And_Overnight_Service_Modelling.git."
date: today
date-format: long
abstract: "Recently, the Canadian government expresses interest in continuous investment in government faculties providing daily shelter and/or overnight services. With the aim to evaluate the validity of predicting the occupied beds at a related faculties at a day, which can reflect the demand of such services at such locations, a multivariate linear regression model is constructed, with the city to Downtown Toronto, and the gender and age set to Mixed Adults. Five predictor variables are used, including two numerical variables, occupancy rate and capacity, and three categorical variables, including classification, service types, and program types. The final results showed likely violations of linearity assumptions such as homoscedasticity and normality of errors, and suggests that we may need to consider either proceed deeper in the linear regression model by adding nonlinear terms for predictor variables, identifying and deleting influential points, and/or consider the weighted-least squares (WLS) method, or consider switching to other more-flexible model types."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
geometry: margin=0.75in
header-includes:
  - \clearpage
---

@@

Downtown Toronto has the most shelters in all the cities of GTA(Greater Toronto Area) in this dataset, so we also conclude that Downtown Toronto is the most representative of all the provided cities, so we then filter out the cleaned data so it only contains shelters in Downtown Toronto.

@@

```{r}
#| label: tbl-table9
#| echo: false
#| warning: false
#| message: false
